The complex network of trophic interactions in a subAntarctic Marine Protected

### 2023-02-04 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Finish Discussion

The species-level analysis aims to describe the species' role in the food web. For this we considered the following properties: (1) betweenness Btw; (2) closeness Cl; (3) trophic similarity TS; (4) topological role TR; and (5) trophic level TL (Table 1). We also studied the relationship between species TL and the other species properties by performing linear regression analyses. Thus, we considered the TL as the dependent variable and the given property as the independent variable, and obtained the coefficients (slope and intercept) for the linear model. Models were fitted using the least squares approach. We also explored the topological role categories with the species TL.
These species-level properties provide a general appropriate description of species' role in empirical complex food webs [@Cirtwill2018].

@@

Taking into account the topological role, 'module specialist' species were the most frequent and presented a wide TL range (1 - 4.77); 'module hub' was constrained to mid-TL species (2.48 - 3.92); 'module connector' from low to mid-TLs (1 - 3.86); and 'network connector', the least frequent, had all of its species in TL = 1, except for one with TL = 3.47 (Figure 4D, see Figure S2 for species' topological roles in a food web graph framework). Here it is important to highlight species of the two latter topological roles, because they are responsible for linking modules and maintaining the connectivity of the food web: 40 species (5 network connectors + 35 module connectors) from 20 different functional groups with a TL range = 1 - 3.86.

@@

Closeness and betweenness are defined as "meso-scale" properties because they consider direct and indirect interactions, therefore describing the focal species’ ability to influence the rest of the species of the food web [@Lai2012].
Closeness quantifies how many steps away species $i$ is from all others in the food web, and is proportional to how rapidly the indirect effects of the focal species can spread to other species in the network [@Scotti2010]. Low-TL consumers arise as important in this regard: species of the zooplankton community, *Calanus* and *Euphausia*, and Brachiopoda. Any perturbation affecting these species, such as mercury [@Fioramonti2022] and microplastics [@Cossi2021], might reach many other species in the food web.
Otherwise, betweenness measures the number of shortest paths between species, providing information on the importance of species as “bridges” for energy transfer: a species with high betweenness takes part in more food chains and therefore affects more energy flows [@Scotti2010]. We have identified the longtail southern cod *Patagonotothen ramsayi* as the most important species in this sense. Moreover, according to our analysis, other species like the Patagonian toothfish *Dissostichus eleginoides*, the Patagonian cod *Salilota australis*, the yellowfin notothen *Patagonotothen guntheri*, and the Patagonian longfin squid *Doryteuthis gahi* should be consider as relevant energy transfers for the ecosystem. All these species have a mid-trophic position in the food web, supporting the 'wasp-waist' control hypothesis for the MPA N-BB [@Riccialdelli2020].

@@

Species' role can be also assessed in a module-based context, where modules are defined as a group of species that interact more frequently among themselves than with species that are not members of the module [@Guimera2005].

Taking into account the topological role, 'module specialist' species were the most frequent and presented a wide TL range (1 - 4.77); 'module hub' was constrained to mid-TL species (2.48 - 3.92); 'module connector' from low to mid-TLs (1 - 3.86); and 'network connector', the least frequent, had all of its species in TL = 1, except for one with TL = 3.47 (Figure 4D, see Figure S2 for species' topological roles in a food web graph framework). Here it is important to highlight species of the two latter topological roles, because they are responsible for linking modules and maintaining the connectivity of the food web: 40 species (5 network connectors + 35 module connectors) from 20 different functional groups with a TL range = 1 - 3.86.

* Topological role. Low and mid-trophic level species (TL = 1 - 3.86) are responsible for maintaining the connectivity of the food web (network connector and module connector). The functional groups represented are: Amphipoda, Bivalvia, Bryozoa, Cnidaria, Cumacea, Decapoda, Detritus, Diatoms, Echinodermata, Fish (bentho-pelagic, demersal, chondrichthyes), Foraminifera, Polychaeta, Porifera, Zooplankton. This shows that the structure of the food web depends on a diversity of species, which at the end comprise the ecosystem's diversity.

* Overall, low and mid-trophic level species arise as crucial in the structure of the MPA Namuncurá - Banco Burdwood food web, since they present the highest betweenness and closeness values, and the most important topological roles. This coincides with a recent study that suggest a wasp-waist trophic structure for the region [@Riccialdelli2020]. However, we also suggest that there exists functional redundancy at mid-trophic levels.
Furthermore, our study points out species of high-trophic levels due to its uniqueness role.

>>>>

The species-level analysis aims to describe the species' role in the food web. For this we considered the following properties: (1) betweenness Btw; (2) closeness Cl; (3) trophic similarity TS; (4) topological role TR; and (5) trophic level TL (Table 1). Topological roles refers to the fact that food webs tend to naturally organize in non-random, modular patterns [@Grilli2016]. Species can play different roles in this respect, according to the pattern of interactions they have within their own module and/or across modules. We computed the topological role for each species, classified as: module hub, species with a relatively high number of interactions, but most within its own module; module specialist, species with relatively few interactions and most within its own module; module connector, species with relatively few interactions mainly between modules; and network connector, species with high connectivity between and within modules [@Guimera2005].

We also studied the relationship between species TL and the other species properties by performing linear regression analyses. Thus, we considered the TL as the dependent variable and the given property (i.e. betweenness, closeness, trophic similarity) as the independent variable, and obtained the coefficients (slope and intercept) for the linear model. Models were fitted using the least squares approach. We also explored the topological role categories with the species TL.
These species-level properties provide a general appropriate description of species' role in empirical complex food webs [@Cirtwill2018].

@@

Taking into account the topological role, 'module specialist' species were the most frequent and presented a wide TL range (1 - 4.77); 'module hub' was constrained to mid-TL species (2.48 - 3.92); 'module connector' from low to mid-TLs (1 - 3.86); and 'network connector', the least frequent, had all of its species in TL = 1, except for one with TL = 3.47 (Figure 4D, see Figure S2 for species' topological roles in a food web graph framework). Here it is important to highlight the two latter topological roles, because they are responsible for linking modules and maintaining the connectivity of the food web: 40 species (5 network connectors + 35 module connectors) from 20 different functional groups with a TL range = 1 - 3.86. The following were the 5 species with a network connector role: Detritus, Diatoms (benthic, centric and pennate), and *Patagonotothen ramsayi*. The 35 species with a module connector role represent these functional groups: Amphipoda, Bivalvia, Brachiopoda, Bryozoa, Cnidaria, Cumacea, Decapoda, Detritus, Diatoms, Dinoflagellates, Echinodermata, Fish (bentho-pelagic, demersal, chondrichthyes), Foraminifera, Polychaeta, Porifera, Pycnogonida, Sea birds, and Zooplankton (see Supplementary Material Table S3 for the identity of the species).

@@

Closeness and betweenness are defined as "meso-scale" properties because they consider direct and indirect interactions, therefore describing the focal species’ ability to influence the rest of the species of the food web [@Lai2012].
Closeness quantifies how many steps away species $i$ is from all others in the food web, and is proportional to how rapidly the indirect effects of the focal species can spread to other species in the network [@Scotti2010]. In the food web of the MPA N-BB, low-TL consumers arise as important in this regard: species of the zooplankton community, *Calanus* and *Euphausia*, and Brachiopoda. Any perturbation affecting these species, such as the already confirmed contaminants mercury [@Fioramonti2022] and microplastics [@Cossi2021; @DiMauro2022] for the area, should be of concern since it might reach many other species in the food web.
Otherwise, betweenness measures the number of shortest paths between species, providing information on the importance of species as “bridges” for energy transfer: a species with high betweenness takes part in more food chains and therefore affects more energy flows [@Scotti2010]. We have identified the longtail southern cod *Patagonotothen ramsayi* as the most important species in this sense. Moreover, according to our analysis, other species like the Patagonian toothfish *Dissostichus eleginoides*, the Patagonian cod *Salilota australis*, the yellowfin notothen *Patagonotothen guntheri*, and the Patagonian longfin squid *Doryteuthis gahi* should be consider as relevant energy transfers for the ecosystem. All these species have a mid-trophic position in the food web, supporting the 'wasp-waist' control hypothesis for the MPA N-BB [@Riccialdelli2020].

@@

Species' role can be also assessed in a module-based context, where modules are defined as a group of species that interact more frequently among themselves than with species that are not members of the module [@Guimera2005]. Among the varying numbers of topological roles in which species can be divided, two are remarkable: 'module connector' and 'network connector'. Here again the longtail southern cod *Patagonotothen ramsayi* is emphasized as an influential species for the connectivity of the food web, which agrees with the suggested 'wasp-waist' control for the MPA N-BB ecosystem [@Riccialdelli2020]. But most importantly, our analysis broadens this issue by pointing out that there are actually other species from a wide range of trophic positions (1 to 3.86), representing 20 different functional groups, that should be considered. Thus, we propose that it is the diversity of species (benthic and pelagic) what maintains the connectivity of the food web, therefore contributing to the trophic structure and ecosystem's stability.
